Denotational Semantics of Gradual Typing using Synthetic Guarded Domain Theory

### 2024-07-12 paper-new/appendix.tex
small changes in appendix

\section{Kleisli Actions}

@@

Recall the notion of quasi-order-equivalence as defined in Definition
\ref{def:quasi-order-equivalent}. The following lemma will be useful in showing
that two relations are quasi-order-equivalent.

@@

The next two lemmas concern quasi-order-equivalence and the functors $\li$ and
$U$.

@@

Lastly, we establish the quasi-order-equivalence for the functors.

@@

Correspondingly, we define a notion of lock-step error ordering and weak
bisimilarity relation for the coinductive delay monad $\delay(\mathbb{N} + {\mho})$:

>>>>

\section{Kleisli Actions}\label{sec:kleisli-actions}

@@

Recall the notion of quasi-equivalence of relations as defined in Definition
\ref{def:quasi-order-equivalent}. The following lemma will be useful in showing
that two relations are quasi-equivalent.

@@

The next two lemmas concern quasi-equivalence and the functors $\li$ and
$U$.

@@

Lastly, we prove quasi-equivalence of relations involving composition and the
functors $U$, $\li$, $\to$ and $\times$.

@@

We define a notion of lock-step error ordering and weak bisimilarity relation
for the coinductive delay monad $\delay(\mathbb{N} + {\mho})$:
